---
title: "ClimateExtract"
output: html_document
date: "2023-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ClimateExtract)
```

## GAEZ data
GAEZ data can be downloaded through its API. To run `gaez_data_extract()`, you need to specify the following parameters: resolution (res); climate model (model); RCP (rcp); time period (time period); indicator (indicator); crop (crop). For instance, if you want to download crop production suitability index, you will run the following code: 

```{r}
path <- "C:/Users/WB495141/OneDrive - WBG/poverty/data/global/crop/gaez/version_4/sxHr0"
res <- "res05" ##resolution
model <- "NorESM1-M" ##climate model
rcp <- "rcp8p5" ##RCP
time <- "2020sH" ##time period
indicator <- "sxHr0" ##Suitability Index
crop <- "whe"
water_supply <- ""
crop_list <- c("whe","brl","mze")
for(c in crop_list) {
  gaez_data_extract(path, res, model, rcp, time, indicator, crop=c, water_supply)
}

```
Here is another example for crop production gap.
```{r qga}
res <- "res07" ##resolution
model <- "" ##climate model
rcp <- "" ##RCP
time <- "2010" ##time period
indicator <- "qga" ##Suitability Index
crop <- "whe"
crop_list <- c("whe","brl","mze")
water_supply <- "T"
gaez_data_extract(path, res, model, rcp, time, indicator, crop="whe", water_supply)
gaez_data_extract(path, res, model, rcp, time, indicator, crop="brl", water_supply)
gaez_data_extract(path, res, model, rcp, time, indicator, crop="mze", water_supply)
for(c in crop_list) {
  gaez_data_extract(path, res, model, rcp, time, indicator, crop=c, water_supply)
}
```
